Project Review - Priyanka

### 2021-12-09 reviews/Project_Review_ESuez_to_MChan.rmd
Review merge
Moved peer-reviews into "review" folder.

---
title: Project Review - Priyanka 
date: "`r file.mtime(knitr::current_input())`"
#bibliography: ../media/references.bib
output: 
  html_document:
    toc_depth: 3
    number_sections: true
---

@@

Title of project:

@@

Name of project reviewer: Priyanka Gannavarapu

# Instructions

Write your comments and feedback below for each section/component of the project. The goal should be to help the author improve their project. Make comments as constructive and actionable as possible. You can provide both criticism and praise.

For each component, pick one summary statement by deleting the ones that do not apply and keeping only the one that you think most closely summarizes a given component.

Make sure your final document compiles/knits into a readable, well-formatted html document.

Delete any sections/text of this template that are not part of your final review document. (Including these instructions.)

@@

The project's context is clearly defined, as is the rationale for investigating this subject. The introduction can have some more information added( previous research)

### Summary assessment (PICK ONE, DELETE THE OTHERS)
*some contextualization and motivation

@@

 The objective is based on the data. But clear hypothesis and questions are needed to make it more clear

### Summary assessment
*question/hypotheses somewhat explained

@@

The data is clearly described, as is the source.

### Summary assessment
* Source and overall structure of data well explained

@@

 More explanation required for data cleaning. Detailed data wrangling would better to understand what is going on! Exploratory analysis should also be presented with more detailed explanation

### Summary assessment
* some weaknesses in wrangling and exploratory component

@@

Data analysis layout has been given well.

* Defensible but not optimal analysis

@@

The flow of the results presented but needs more commentary and detailed description of what the findings are

@@

* Results are presented ok, with room for improvement

@@

Discussion section can be worked on a little. Presenting the finding and discussing the previous literature would be a solution. Checking if the results are in line or different from previous studies

### Summary assessment
* Minor parts wrong, missing or unclear

@@

_Add any other comments regarding the different aspects of the project here. Write anything you think can help your classmate improve their project._

@@

The discussion portion can be worked on a little by mentioning previous research and comparing if the findings of this study are in line or is their any difference. If yes, what could the reasons be for the change in the results.

### Summary assessment
mostly clear, but some confusing parts

@@

 The documentation needs more clearer explanation and should be distinct to show what information is in which folder. Needs more detailed comments in the specific files

### Summary assessment
* decently documented with some gaps

@@

Reproducible results

@@

Questions and hypothesis were addressed. More alternatives can be considered

### Summary assessment
* decent level of thoroughness

@@

_Add any other comments regarding the overall project here. Write anything you think can help your classmate improve their project.

Great project considering the situation we are in. all results reproducible and no manual intervention was needed.

>>>>

@@

Title of project:"MADA Data Analysis Project"

@@

Name of project reviewer: Ehsan Suez

@@

**
Precisely defined. I would personally want some details in introduction.**

### Summary assessment (PICK ONE, DELETE THE OTHERS)
**some contextualization and motivation**

@@

**I think all three aims were clearly presented here**

** question/hypotheses fully clear **

@@

I think the data was clearly described, as well as the source of the data.

** source and overall structure of data well explained **

@@

I think you have done a great job with data wrangling. But I would suggest to add more comments for the readers to understand the way you were thinking while doing those particular steps.

** some weaknesses in wrangling and exploratory component **

@@

As per my knowledge, I think the analysis were pretty sound. And the way the analysis was presented, was great. There is always room for improvement in general, but I think you did great here.

### Summary assessment
* strong and reasonable analysis

@@

The result presentation was good. Tables and figures were easy to understand.

@@

* results are very well presented

@@

I think the finding was discussed on a good level. You can add some more points there (detailing basically).

* strong, complete and clear discussion

@@

@@

We;; structured, well labeled. Some files in the analysis folder could have been named a bit better.

** mostly clear, but some confusing parts (e.g. useless files, things in the wrong folders) **

@@

Overall well documented. But I would suggest having a clearer way of labeling files and organizing them.

* decently documented with some gaps

@@

I was able to rerun the whole thing.

@@

WRITE YOUR FEEDBACK HERE

* strong level of thorougness

@@

_Add any other comments regarding the overall project here. Write anything you think can help your classmate improve their project._
